WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-07-13 ms.tex
Fix typo

\paragraph*{2016} The second observing run, ``O1'', with the two between Advanced \acs{LIGO} detectors, upgraded to a \ac{BNS} range of 80\nobreakdashes--120\,Mpc, operated jointly with the newly commissioned Advanced Virgo detector (``V''), operating at a range of 20\nobreakdashes--60\,Mpc. The run is envisioned as lasting for six months in 2016\nobreakdashes--2017. The detectors are assumed to have random and independent 80\% duty cycles. Consequently, all three detectors (``HLV'') are in science mode about half of the time, with the remaining time divided roughly equally between each of the possible pairs (``HL'', ``HV'', or ``LV'') and one or fewer detectors (at least two \ac{GW} facilities are required for a detection). Virgo's range is assumed to be somewhat less than \acs{LIGO}'s because its commissioning timetable is about a year behind. Although the simulated signals are generally to weak in Virgo to trigger the matched\nobreakdashes-filter pipeline and contribute to \emph{detection}, even these sub\nobreakdashes-threshold signals aid in position reconstruction with LALINFERENCE by lifting degeneracies. As a result, the median 90\% credible area decreases to about 200\,deg$^2$.

>>>>

\paragraph*{2016} The second observing run, ``O1'', with the two between Advanced \acs{LIGO} detectors, upgraded to a \ac{BNS} range of 80\nobreakdashes--120\,Mpc, operated jointly with the newly commissioned Advanced Virgo detector (``V''), operating at a range of 20\nobreakdashes--60\,Mpc. The run is envisioned as lasting for six months in 2016\nobreakdashes--2017. The detectors are assumed to have random and independent 80\% duty cycles. Consequently, all three detectors (``HLV'') are in science mode about half of the time, with the remaining time divided roughly equally between each of the possible pairs (``HL'', ``HV'', or ``LV'') and one or fewer detectors (at least two \ac{GW} facilities are required for a detection). Virgo's range is assumed to be somewhat less than \acs{LIGO}'s because its commissioning timetable is about a year behind. Although the simulated signals are generally too weak in Virgo to trigger the matched\nobreakdashes-filter pipeline and contribute to \emph{detection}, even these sub\nobreakdashes-threshold signals aid in position reconstruction with LALINFERENCE by lifting degeneracies. As a result, the median 90\% credible area decreases to about 200\,deg$^2$.
